Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
pf <- read.csv('pseudo_facebook.tsv',sep = '\t')
qplot(x = age, y = friend_count, data = pf)
```

***

#### What are some things that you notice right away?
Response: Younger users have a lot of friends. There are users who lie about their ages (vertical bars)
***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(aes(x = age, y = friend_count),data=pf) + xlim(13,90) + geom_point()

summary(pf$age)
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x = age, y = friend_count),data = pf) + 
  geom_jitter(alpha=1/20) +
  xlim(13, 90)
```

#### What do you notice in the plot?
Response: Friend count for young users is not as high as before. Also the cap for age is set at 69.
***

### Coord_trans()
Notes:

```{r Coord_trans()}

```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}
ggplot(aes(x = age, y = friend_count),data = pf) + 
  geom_jitter(alpha=1/20, position = position_jitter(h = 0)) +
  xlim(13, 90) +
  coord_trans(y = 'sqrt')
```

#### What do you notice?
We can see threshold of friend count above which there are very few users.
***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
qplot(x = age, y = friendships_initiated, data = pf)

ggplot(aes(x = age, y = friendships_initiated),data=pf) + xlim(13,90) + geom_point()

ggplot(aes(x = age, y = friendships_initiated),data = pf) + 
  geom_jitter(alpha=1/10)

ggplot(aes(x = age, y = friendships_initiated),data = pf) + 
  geom_point(alpha=1/10, position = position_jitter(h = 0)) +
  coord_trans(y = 'sqrt')
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
install.packages('dplyr')
library(dplyr)

age_groups <- group_by(pf, age)
pf.fc_by_age <- summarise(age_groups,
                          friend_count_mean = mean(friend_count),
                          friend_count_median = median(friend_count),
                          n = n())
pf.fc_by_age <- arrange(pf.fc_by_age, age)
head(pf.fc_by_age)
```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(age, friend_count_mean), data = pf.fc_by_age) + 
  geom_line()
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(aes(age, friend_count), data=pf) + 
  coord_cartesian(xlim = c(13,70), ylim = c(0,1000)) + 
  geom_point(alpha = .05, position = position_jitter(h = 0), color = 'orange') +
  coord_trans(y = 'sqrt') +
  geom_line(stat = 'summary', fun.y = mean) +
  geom_line(stat = 'summary', fun.y = quantile, fun.args=list(probs=0.1), 
            linetype = 2, color = 'blue') +
  geom_line(stat = 'summary', fun.y = quantile, fun.args=list(probs=0.5), 
            linetype = 2, color = 'blue') +
  geom_line(stat = 'summary', fun.y = quantile, fun.args=list(probs=0.9), 
            linetype = 2, color = 'blue')
```

#### What are some of your observations of the plot?
Response: Having more than 1000 friends is quite rare.
***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
cor.test(pf$age, pf$friend_count, method = 'pearson')
with(pf, cor.test(age, friend_count, method = 'pearson'))
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response: -0.02740737

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(pf, age <= 70), cor.test(age, friend_count), method = 'pearson')
```

***

### Correlation Methods
Notes: Pearson, Spearman, and Kendall

***

## Create Scatterplots
Notes:

```{r}
ggplot(aes(x = www_likes_received, y = likes_received), data = pf) + geom_point()
```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
ggplot(aes(x = www_likes_received, y = likes_received), data = pf) + geom_point() +
  xlim(0, quantile(pf$www_likes_received, 0.95)) +
  ylim(0, quantile(pf$likes_received, 0.95)) +
  geom_smooth(method = 'lm', color = 'red')
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}
cor.test(pf$www_likes_received, pf$likes_received, method = 'pearson')
```

Response: 0.948

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
data("Mitchell")
?Mitchell
```

Create your plot!

```{r Temp vs Month}
ggplot(aes(x = Temp, y = Month), data = Mitchell) + geom_point()
```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot. 0

b. What is the actual correlation of the two variables? 0.057
(Round to the thousandths place)

```{r Noisy Scatterplots}
cor.test(Mitchell$Temp,Mitchell$Month)
```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}
ggplot(data = Mitchell, aes(x = Month, y = Temp)) +
  geom_point() +
  scale_x_discrete(breaks = seq(0,203,102))
```

***

### A New Perspective

What do you notice?
Response: Cyclical patterns (almost like a sin or cosin graph)

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
ggplot(aes(x=age, y=friend_count_mean), data = pf.fc_by_age) +
  geom_line()

head(pf.fc_by_age, 10)
pf.fc_by_age[17:19, ]
 ```

***

### Age with Months Means

```{r Age with Months Means}
pf$age_with_month <- pf$age + (12 - pf$dob_month) / 12
```

Programming Assignment
```{r Programming Assignment}
library(dplyr)
pf.fc_by_age_months <- pf %>%
  group_by(age_with_month) %>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age_with_month)
head(pf.fc_by_age_months)
```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}
ggplot(aes(x = age_with_month, y = friend_count_mean),
       data = subset(pf.fc_by_age_months, age_with_month < 71)) +
  geom_line()
```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}
p1 <- ggplot(aes(x = age, y = friend_count_mean),
       data = subset(pf.fc_by_age, age < 71)) +
  geom_line() + geom_smooth()

p2 <- ggplot(aes(x = age_with_month, y = friend_count_mean),
       data = subset(pf.fc_by_age_months, age_with_month < 71)) +
  geom_line() + geom_smooth()

p3 <- ggplot(aes(x = round(age / 5) * 5, y = friend_count),
             data = subset(pf, age < 71)) +
  geom_line(stat = 'summary', fun.y = mean)

library(gridExtra)
grid.arrange(p2,p1,p3,ncol=1)
```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection: Explore the relationships between 2 variables. Visualization using scatterplot. Benefits of correlation coeffcient. Use jitter and alpha to avoid overfitting.

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

